### 2015-07-14 ids-fusion.tex
Editing --- simpler sentence.
Not sure if there's an actual change here --- git funniness.

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left
% TODO restore to QR15
%as an exercise for
 to
the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches
% TODO restore to QR15
% --- network (NIDS) vs.\
% host-based (HIDS), signature vs.\ anomaly-based --- 
bring different
strengths and weaknesses, and have different ``fields of view.'' For example, local
privilege escalation attacks may be invisible to a NIDS; HIDS systems are more
accurate for many purposes, but impose higher administrative burdens because
they must be scattered around the defended network, rather that centrally
deployed like NIDS.  Signature-based IDSes provide fewer false positives, but
are more likely to be blind to zero-day attacks than anomaly-based systems.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
% Briefly, more accurate \idses have significantly higher software
% administration burdens, and there is an inevitable tradeoff between
% false positives and false negatives.
% This tradeoff applies for all of the different varieties of IDS,
% for example NIDS or HIDS, signature-based, anomaly-detecting, various
% hybrids.

@@

% New paragraph to address
% [[file:todo.txt::*Review%201:%20learned%20or%20hand-made%20domains?][Review 1: learned or hand-made domains?]]
% and [[file:todo.txt::*Review%201:%20Hand-made%20vs.%20generated][Review 1: Hand-made vs. generated]]
Some of our reviewers expressed the concern that we would have difficulty
\emph{modeling} the rare events in \ids fusion.  This problem does not, in fact,
arise, for three reasons.  One is that these attack events are not rare in the
world: they are rare with respect to our sampling rate.  As we point out above,
if we are sampling individual packets, the probability of any attack is
vanishingly small, but that doesn't mean that attacks are rare at the
``macroscopic'' level.  Second, our causal models are limited to models of
sensing and fusion, part/whole, and class/subclass relations.  These models are
very simply generated by rules.  Finally, the \ids developers provide us initial
ontologies of events implicitly with their rules.  Our knowledge engineering
aims at smoothing inconsistencies between these implicit ontologies, and
extending causal models by identifying cases where \ids developers have
provided incorrect intuitions about the events their systems detect.
At any rate, this concern is not relevant to the evaluation of the uncertainty
calculus, which is our focus in this paper.

Users regularly ignore or disable their {\idses}, unable to absorb
massive streams of false alarms.
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
% ~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
card records~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem. It shows how our earlier system was able to winnow
the 
flow of reports in a small corporate network over a day of operation~\anoncite{goldman:09Scyllarus}.
% Data reduction must join building a comprehensive overview
% and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}

>>>>

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left
% WONTFIX restore to QR15
%as an exercise for
 to
the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches
% WONTFIX restore to QR15
% --- network (NIDS) vs.\
% host-based (HIDS), signature vs.\ anomaly-based --- 
bring different
strengths and weaknesses, and have different ``fields of view.'' For example, local
privilege escalation attacks may be invisible to a NIDS; HIDS systems are more
accurate for many purposes, but impose higher administrative burdens because
they must be scattered around the defended network, rather that centrally
deployed like NIDS.  Signature-based IDSes provide fewer false positives, but
are more likely to be blind to zero-day attacks than anomaly-based systems.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
% Briefly, more accurate \idses have significantly higher software
% administration burdens, and there is an inevitable tradeoff between
% false positives and false negatives.
% This tradeoff applies for all of the different varieties of IDS,
% for example NIDS or HIDS, signature-based, anomaly-detecting, various
% hybrids.

@@

% New paragraph to address
% [[file:todo.txt::*Review%201:%20learned%20or%20hand-made%20domains?][Review 1: learned or hand-made domains?]]
% and [[file:todo.txt::*Review%201:%20Hand-made%20vs.%20generated][Review 1: Hand-made vs. generated]]
Some of our reviewers expressed the concern that we would have difficulty
\emph{modeling} the rare events in \ids fusion.  There are three
reasons when this problem does not
arise.  One is that these attack events are not rare in the
world: they are rare with respect to our sampling rate.  As we point out above,
if we are sampling individual packets, the probability of any attack is
vanishingly small, but that doesn't mean that attacks are rare at the
``macroscopic'' level.  Second, our causal models are limited to models of
sensing and fusion, part/whole, and class/subclass relations.  These models are
very simply generated by rules.  Finally, the \ids developers provide us initial
ontologies of events implicitly with their rules.  Our knowledge engineering
aims at smoothing inconsistencies between these implicit ontologies, and
extending causal models by identifying cases where \ids developers have
provided incorrect intuitions about the events their systems detect.
At any rate, this concern is not relevant to the evaluation of the uncertainty
calculus, which is our focus in this paper.

Users regularly ignore or disable their {\idses}, unable to absorb
massive streams of false alarms.
``Users attending an 'ABCs of IDS' event at London's City University yesterday
  said more the 80 per cent of the alerts they received were false, with one
  citing 60 alerts he had received about non-existent problems that morning at
  0300''~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
card records~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem. It shows how our earlier system was able to winnow
the 
flow of reports in a small corporate network over a day of operation~\anoncite{goldman:09Scyllarus}.
% Data reduction must join building a comprehensive overview
% and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}
